### 2014-03-02 paper/intro.tex
Flow it
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Information flow control (IFC) is a promising technique for addressing these
problems, by tracking the flow of sensitive data through a system and
confining untrusted code so that it cannot exfiltrate data, except as
per a information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit information
flow control on top of it.  A key challenge in the design of these
systems is ensuring they can be implemented efficiently: when the
semantics specify that information flow must be tracked at a
fine-grained level, e.g., per value in the system,  it can lead to
impractical runtime overheads even for ordinary operations.

An alternative to this is a more \textit{coarse-grained} approach
to IFC by trading off precision for efficiency.  Here, computational
units are associated with a floating label which protects all data
in this unit.
A recent example dubbed SWAPI adds IFC to the web by extending
Javascript with coarse-grained IFC by identifying web workers as
an existing computational unit.  Communication between workers can
efficiently be mediated in an IFC aware way to ensure a notation
non-interference, where sensitive workers cannot influence the
computations in less sensitive workers.

>>>>

Information flow control (IFC) is a promising technique for addressing these
problems, by tracking the flow of sensitive data through a system and
confining untrusted code so that it cannot exfiltrate data, except as
per a information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit dynamic information
flow control on top of it.  A key challenge in the design of these
systems is ensuring they can be implemented efficiently: when the
semantics specify that information flow must be tracked at a
fine-grained level, e.g., per value in the system,  it can lead to
impractical runtime overheads even for ordinary operations.

One alternative is a \textit{coarse-grained} approach to IFC.  Here,
computational units are associated with a floating label which protects
all data in this unit.  A recent system named SWAPI adds IFC to the
browser by identifying \emph{web workers} as an existing computational
unit.  Communication between workers can efficiently be mediated in an
IFC aware way to ensure non-interference, where sensitive workers cannot
influence the computations in less sensitive workers.
